Software engineering landscape is undergoing a major paradigm shift driven by the usage of Large Language Models (LLMs) and AI-assisted programming agents due to which we can see a significant acceleration in software deployment lifecycles and the exponential growth of codebase complexities. However this fundamental shift in how software is developed has introduced various new systemic risks to long term software health.
While AI generated code increase functional delivery speeds, it often introduces subtle structural vulnerabilities, architectural inconsistencies, and latent technical debt that evades immediate detection \parencite{human_written_vs_ai_generated_code_2025}. These issues can accumulate over time, leading to significant degradation in software quality, maintainability, and security. Traditional software quality assessment mechanisms which rely heavily on manual human reviews and static, point-in-time rule checking are becoming increasingly inadequate in this new landscape. They fail to capture the dynamic, evolving nature of software quality in AI-augmented development environments, where codebases are continuously changing and growing in complexity.

Software Quality is defined theoretically by international standards such as the ISO/IEC 25010 standard, which outlines non-functional characteristics including Maintainability, Security, Performance Efficiency, and Reliability \parencite{isoiec25010_quality_model_emergentmind}. Operationally, these characteristics are measured using static code analysis tools. textbf{SonarQube} has established itself as the industry standard for continuous code quality inspection which utilizes a comprehensive set of rules to detect bugs, code smells and security vulnerabilities. \parencite{sonarqube_metrics_definition}. Yet this conventional static code analyis remains retrospective and evaluates the codebase at a discrete point in time, identifying existing flaws but fails to anticipate how AI-generated code will degrade quality over time.

To address the limitations of retrospective analysis and to accommodate  the usage of AI in software development, there is a critical need for intelligent, predictive analytics platforms. The proposed research project, \textbf{Deltx}, aims to architect an expert-level static analysis and predictive analytics platform built on top of SonarQube engine. By integrating advanced machine learning techniques for stylometric AI code detection and utilizing state-of-the-art Transformer-based time-series forecasting architectures, Deltx seeks to transform static, isolated metrics into proactive, explainable quality trajectories.

\section{Problem Statement}

The Software Engineering domain faces a critical research gap in predicting and managing long-term software quality, particularly with the growing adoption of AI-generated code.” \parencite{developers_self_declaration_ai_generated_code}. This project addresses four interrelated, foundational problems within this domain:

\subsubsection*{Issue 1: Invisibility of AI-Generated Structural Decay}

Current static analysis tools process all source code uniformly and fails to distinguish between human-authored code and AI-generated code. AI models which are trained on vast but generalized contexts often generate code that is functionally correct in isolation but may introduce structural issues when integrated into larger codebases. Recent empirical analyses indicate that AI-generated pull requests contain up to 1.7 times more structural issues than human-authored equivalents, leading to higher issue densities and rapid technical debt accumulation \parencite{coderabbit_ai_vs_human_code_generation_report}. Without the ability to identify AI-generated code, organizations cannot apply targeted verification, nor can predictive models accurately weigh the decay risks associated with synthetic authorship.

\subsubsection*{Issue 2: Semantic Gap in Software Quality Metrics}

SonarQube generates granular rule-based outputs (cyclomatic complexity, code smells, debt ratios) \parencite{sonarqube_metrics_definition}. However, there is a distinct semantic gap between these raw, disjointed metrics and high-level business risk frameworks. TConverting raw software metrics into balanced and meaningful quality dimensions such as Correctness, Maintainability, Security, and Efficiency, remains an unsolved architectural challenge. Existing aggregation approaches often struggle to handle conflicting signals effectively, where a large number of minor formatting issues can end up outweighing a single critical security vulnerability in the overall evaluation. \parencite{software_quality_metrics_aggregation_industry}.

\subsubsection*{Issue 3: Retrospective Nature of Static Analysis}

Platforms like SonarQube provide point-in-time snapshots of codebase health but lack time-series forecasting capability to predict how code quality will evolve across future commits \parencite{sonarcommunity_historical_data}. Without this capability, engineering teams are forced to a reactive posture that addresses debt only after it breaches critical thresholds, rather than proactively managing codebase health based on predicted degradation \parencite{software_service_supporting_software_quality_forecasting}.

\subsubsection*{Issue 4: Lack of Interpretability in Predictive Metrics}

There is a profound lack of interpretability in predictive software metrics. The application of deep learning in software engineering often results in opaque, ``black-box'' predictions. If a predictive system forecasts a severe decline in software security, it must concurrently provide human-readable insights explaining precisely why he forecast was made, identifying the specific historical metrics, code churn events, or AI-code influxes driving the forecast. \parencite{perspective_on_xai_methods_shap_and_lime}.

\vspace{0.5cm}

By systematically addressing these four challenges, Deltx will advance software engineering theory by combining stylometric AI detection, vulnerability assessment, advanced time-series forecasting, and Explainable AI into a unified, rigorous framework.